### 2021-11-21 draft.tex
Deploying to gh-pages from @ gottacatchenall/thesis_proposal@2e20d4341ce2e47ec842b54e85a9477d1e795a64 🚀

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\tightlist
\item
  we got a tree and SDMs. See appendix figure.
\end{enumerate}

@@

Promoting landscape connectivity is important to mitigate the effects of
land-use change on Earth's biodiversity. However, the practical
realities of conservation mean that there is a limitation on how much we
can modify landscapes in order to do this. So what is the best place to
put a corridor given a constraint on how much surface-area you can
change in a landscape? This is the question this chapter seeks to
answer. Models for inferring corridor locations have been developed, but
are limited in that are not developed around promoting some element of
ecosystem function, but instead by trying to find the path of least
resistance in an existing landscape from a derived resistance surface
(Peterman 2018).

This chapter proposes a general algorithm for choosing corridor
placement to optimize a measurement of ecosystem functioning derived
from simulations run on each proposed landscape modification.

@@

@@

\hypertarget{appendix}{%
\section{Appendix}\label{appendix}}

\begin{figure}
\centering
\includegraphics{./figures/trees.png}
\caption{trees}
\end{figure}

>>>>

We have phylogenies and species distributions models.

\begin{figure}
\centering
\includegraphics{./figures/trees.png}
\caption{Phylogeny for both bumblebee species (left) and flower species
(right)}
\end{figure}

\begin{figure}
\centering
\includegraphics{./figures/sample_sdm.png}
\caption{Example SDM for \emph{Archillea millefolium}}
\end{figure}

@@

As land-use change has caused many habitats to become fragmented and
patchy, promoting landscape connectivity has become of significant
interest to mitigate the effects of this change on Earth's biodiversity.
However, the practical realities of conservation mean that there is a
limitation on how much we can modify landscapes in order to do this. So
what is the best place to put a corridor given a constraint on how much
surface-area you can change in a landscape? This is the question this
chapter seeks to answer. Models for inferring corridor locations have
been developed, but are limited in that are not developed around
promoting some element of ecosystem function, but instead by trying to
find the path of least resistance in an existing landscape from a
derived resistance surface (Peterman 2018). This chapter proposes a
general algorithm for choosing corridor placement to optimize a
measurement of ecosystem functioning derived from simulations run on
each proposed landscape modification.

@@

We then use simulated annealing to explore the search space of possible
modifications to estimate the modification that maximizes the time-until
extinction of simulated metapopulation dynamics under that hypothetical
modified landscape.

@@
